Analysis of the Anomalous Doppler Effect from Quantum Theory to Classical Dynamics Simulations

### 2025-05-22 paper modification/CPB-tex-template/CPB manuscript/Latex_manuscript/paper_v2.tex
add new

\textbf{PACS: 33.35.+r, 02.60.Cb,  03.65.-w，12.20.-m} %no more than four PACS codes should be provided: check https://cpb.iphy.ac.cn/UserFiles/File/PACS2010Regular-Edition.pdf

>>>>

\textbf{PACS: 33.35.+r, 02.60.Cb,  03.65.-w, 12.20.-m} %no more than four PACS codes should be provided: check https://cpb.iphy.ac.cn/UserFiles/File/PACS2010Regular-Edition.pdf
